---
title: "Software Knowledge Graph Community Analysis"
output: html_notebook
---


```{r, echo=FALSE, echo=FALSE}

#
# Packages ----
#


library(tidyverse)


#
# Settings ----
#


# We kept our data in a synced folder outside the repo.
# Since paths depend on user & machine, we define them in settings.R.
# Example content of settings.R:
# path.root <- "C:/Users/Jakob/sciebo/Projekte/SoftwareKG/"
# path.data <- paste0(path.root,"data/")
# path.network <- paste0(path.root,"network/")
source("settings.R")

theme_set(theme_bw(base_size=12))

colours = rev(c("#F8766D", "#619CFF", "#48d993", "#C77CFF",
                "#999999", "#f2b602", "#0072B2", "#D55E00", 
                "#9abd8c", "#CF2355", "#56B4E9", "#61295c",
                "#009E73","#61295c", "#56B4E9", "#CF2355", 
                "#996953", "#8787e6", "#2E27E6","#F8766D", 
                "#619CFF"))


#
# Data ----
#

com_nodes <- read_csv(paste0(path.network, "com_nodes.csv"))
com_communities <- read_csv(paste0(path.network, "com_communities.csv"))


```

# Overview

Using the Leiden algorithm on conditional probabilities of cooccurrences, we found 34 communities:

- 11 pairs, i.e. communities consisting of two nodes each. 
- 17 communities consituted by 3 to 49 nodes.
- 6 large communities containing fifty nodes or more. 

```{r}

com_communities %>% 
  count(n_nodes) %>% 
  print()

com_communities %>% 
  mutate(top_degree_in = str_trunc(top_degree_in,30)) %>%
  mutate(top_degree_out = str_trunc(top_degree_out,30)) %>% 
  select(community_no,n_nodes, density, top_degree_in, top_degree_out) %>% 
  print()

```


# Software types
```{r}

# Software types
com_nodes %>%  
  count(community_no, softwaretype) %>% 
  group_by(community_no) %>% 
  mutate(p = n / sum(n)) %>% 
  ungroup() %>% 
  
  ggplot(aes(y=n,x=community_no,fill=softwaretype)) +
  geom_col() 

```


# Degrees by software types
com_nodes %>%  
  filter(as.numeric(community_no) <= 15) %>% 
  pivot_longer(cols=starts_with("degree"), names_to="degree") %>% 
  ggplot(aes(x=softwaretype, y=value, fill=degree)) +

  geom_boxplot() +
  facet_wrap(~community_no, ncol=3) +
#  scale_y_log10() +
  coord_flip()
  

# Concepts


```{r}

pl <- com_nodes %>% 
  pivot_longer(
    cols=starts_with("con_"),
    names_to = "concepts_name",
    names_prefix="con_",
    values_to = "concepts_n"
  ) %>% 
  
  group_by(community_no, concepts_name) %>%
  summarize(concepts_n = sum(concepts_n)) %>% 
  ungroup() %>% 
  
  group_by(community_no) %>% 
  mutate(concepts_p= concepts_n / sum(concepts_n)) %>% 
  ungroup() %>% 
  
  mutate(concepts_name = fct_reorder(concepts_name,-concepts_p,mean)) %>%
  mutate(concepts_no = as.numeric(concepts_name)) %>% 
  mutate(concepts_name = paste0(concepts_no," ",concepts_name)) %>%
  mutate(concepts_name = fct_reorder(concepts_name,concepts_no,mean)) %>%
  mutate(concepts_label = ifelse(concepts_p > 0.1, concepts_no,"")) %>% 
  
  
  ggplot(aes(y=concepts_p,x=community_no,fill=concepts_name)) +
  geom_col() +
  geom_text(
    aes(label=concepts_label),
    position = position_stack(vjust = .5),
    size=3, color="white"
  ) +

  scale_fill_manual(values=colours) +
  theme(legend.position = "bottom")

print(pl)

```

